### 2024-09-18 manuscript/tables/table_summary_methods.tex
Combine table 7 and 8

% latex table generated in R 4.4.0 by xtable 1.8-4 package
% Tue Jun 25 10:25:27 2024
\begin{table}[H]
\centering
\caption{Summary of the methods and spatial scales used to estimate the density of each vertebrate species on Bylot Island, and how abundance was extrapoated at the landscape scale.} 

@@

\begin{tabularx}{\textwidth}{lllll}
Species & Sampling method & Reference species & Sampling scale & Spatial extrapolation \\ 
king eider & nest sampling &  & 4x2km plot & wetlands \\ 
  long tailed duck & nest sampling &  & 4x2km plot & wetlands \\ 
  king eider & relat. abund. (incidental obs.) & red-throated loon & study area &  \\ 
  long tailed duck & relat. abund. (incidental obs.) & red-throated loon & study area &  \\ 
  Pacific loon & nest sampling &  & study area &  \\ 
  red-throated loon & nest sampling &  & study area &  \\ 
  cackling goose & nest sampling &  & study area &  \\ 
  snow goose & nest sampling &  & camp 2 & goose colony \\ 
  snow goose & vertebrate count transects &  & lowland & goose colony \\ 
  snow goose & snow goose point counts &  & lowland & goose colony \\ 
  tundra swan & nest sampling &  & study area &  \\ 
  rough-legged hawk & nest sampling &  & study area &  \\ 
  peregrine falcon & nest sampling &  & study area &  \\ 
  snowy owl & nest sampling &  & study area &  \\ 
  rock ptarmigan & nest sampling &  & 4x2km plot & all habitats \\ 
  sandhill crane & nest sampling &  & 4x2km plot & transects \\ 
  American golden-plover & distance sampling &  & lowland & transects \\ 
  black-bellied plover & relat. abund. (transects) & A. golden-plover & lowland & transects \\ 
  black-bellied plover & relat. abund. (incidental obs.) & A. golden-plover & study area &  \\ 
  common-ringed plover & nest sampling &  & study area &  \\ 
  ruddy turnstone & relat. abund. (transects) & Baird’s sandpiper & lowland & transects \\ 
  ruddy turnstone & relat. abund. (incidental obs.) & Baird’s sandpiper & study area &  \\ 
  red knot & relat. abund. (transects) & Baird’s sandpiper & lowland & transects \\ 
  red knot & relat. abund. (incidental obs.) & Baird’s sandpiper & study area &  \\ 
  pectoral sandpiper & relat. abund. (transects) & Baird’s sandpiper & lowland & transects \\ 
  pectoral sandpiper & relat. abund. (incidental obs.) & Baird’s sandpiper & study area &  \\ 
  Baird’s sandpiper & nest sampling &  & 2x1km plot & transects \\ 
  white-rumped sandpiper & relat. abund. (transects) & Baird’s sandpiper & lowland & transects \\ 
  white-rumped sandpiper & relat. abund. (incidental obs.) & Baird’s sandpiper & study area &  \\ 
  buff-breasted sandpiper & relat. abund. (transects) & Baird’s sandpiper & lowland & transects \\ 
  buff-breasted sandpiper & relat. abund. (incidental obs.) & Baird’s sandpiper & study area &  \\ 
  red phalarope & relat. abund. (transects) & Baird’s sandpiper & lowland & transects \\ 
  red phalarope & relat. abund. (incidental obs.) & Baird’s sandpiper & study area &  \\ 
  glaucous gull & nest sampling &  & study area &  \\ 
  long-tailed jaeger & nest sampling &  & qarlikturvik & mesic habitat \\ 
  parasitic jaeger & maximum banded individual &  & study area &  \\ 
  parasitic jaeger & nest sampling &  & study area &  \\ 
  common raven & nest sampling &  & study area &  \\ 
  common raven & relat. abund. (incidental obs.) & Parasitic jaeger & study area &  \\ 
  horned lark & relat. abund. (transects) & lapland longspur & lowland & transects \\ 
  horned lark & relat. abund. (incidental obs.) & lapland longspur & study area &  \\ 
  American pipit & relat. abund. (transects) & lapland longspur & lowland & transects \\ 
  American pipit & relat. abund. (incidental obs.) & lapland longspur & study area &  \\ 
  lapland longspur & nest sampling &  & 2x1km plot & transects \\ 
  snow bunting & relat. abund. (transects) & lapland longspur & lowland & transects \\ 
  snow bunting & relat. abund. (incidental obs.) & lapland longspur & study area &  \\ 
  brown lemming & capture marking recapture &  & two 11 ha grids & wet and mesic hab. \\ 
  collared lemming & capture marking recapture &  & two 11 ha grids & wet and mesic hab. \\ 
  arctic hare & incidental observations & Arctic fox & study area &  \\ 
  ermine & relat. abund. (testimonials) &  & study area &  \\ 
  arctic fox & home range (movement track.) &  & study area &  \\ 
\end{tabularx}

@@

\end{table}

>>>>

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Tue Sep 10 15:05:42 2024
\begin{longtable}{|p{0.11\textwidth}|p{0.07\textwidth}|p{0.21\textwidth}|p{0.06\textwidth}|p{0.18\textwidth}|p{0.035\textwidth}|p{0.037\textwidth}|p{0.037\textwidth}|p{0.035\textwidth}|p{0.017\textwidth}|p{0.14\textwidth}|}
\caption{Summary of the mean (± standard deviation) and minimum and maximum (when available) annual abundance of vertebrate species for the whole Bylot Island study area (389 km2).  In some cases, several independent approaches have been used to estimate the abundance of a species as a proxy for uncertainty. We did not quantitatively assess uncertainty on each estimate of species abundance. However, we provide a qualitative measure of method quality based on the quality and quantity of data available, method used for extrapolation (if necessary), and in some cases, from the fit of statistical models to estimate density. We also provided coarse confidence intervals derived from consultation with field experts at the study site.} \\ 
{\textbf{Species}} & {\textbf{Estimate}} & {\textbf{Method}} & {\textbf{Method quality}} & {\textbf{Justification}} & {\textbf{Min}} & {\textbf{Max}} & {\textbf{Mean}} & {\textbf{sd}} & {\textbf{n}} & {\textbf{Expert based confidence interval}} \\ 
snow goose & 1999-2009 & Nest monitoring plots extrapolated to mean goose colony area & low & Relatively small sample size and uncertainty on goose colony area  & 2505 & 35404 & 18129 & 11037 &  11 & several thousands to few tens of thousands \\ 
snow goose & 2010-2019, 2022-2023 & Intensive study area-wide monitoring based on several
methods and annual colony outline & high & Multiple independent methods and annual colony outline & 8687 & 49076 & 31852 & 12092 &  12 & thousands \\ 
snowy owl & 1996-2011 & Extrapolation from intensive nest monitoring (111 km2,
R2=0.99, p$<$0.0001, n=10) & high & Strong correlation with study area-wide nest density &   0 &  67 & 15 & 24 &  16 & units to few tens \\ 
snowy owl & 2012-2019, 2022-2023 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &   0 & 144 & 17 & 45 &  10 & units to few tens \\ 
glaucous gull & 2004-2016 & Extrapolation from intensive nest monitoring (111 km2,
R2=0.84, p=0.16, n=4) & high & Strong correlation with study area-wide nest density &  59 &  80 & 73 & 6 &  13 & few tens \\ 
glaucous gull & 2017-2019, 2022 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &  60 &  80 & 71 & 9 &   4 & few tens \\ 
peregrine falcon & 2013-2019, 2022 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &   8 &  12 & 10 & 1 &   8 & units \\ 
rough-legged hawk & 2007-2012 & Extrapolation from intensive nest monitoring (111 km2,
R2=0.99, p$<$0.0001, n=8) & high & Strong correlation with study area-wide nest density &   3 &  59 & 20 & 19 &   8 & few tens \\ 
rough-legged hawk & 2013-2019, 2022 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &   0 &  66 & 30 & 29 &   8 & few tens \\ 
American golden-plover & 2014-2019, 2022-2023 & Distance sampling throughout lowland (313 km2) & high & Large sample size & 306 & 1040 & 774 & 275 &   8 & hundreds \\ 
cackling goose & 1996-2016 & Extrapolation from exponential model of growth (R2=0.74,
p=0.15, n=5) & moderate & Strong correlation with opportunistic nest monitoring &   2 & 158 & 31 & 41 &  23 & units to tens \\ 
cackling goose & 2017-2019, 2022-2023 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &  80 & 214 & 138 & 50 &   5 & few tens \\ 
Arctic fox & mean & Derived from extensive fox home range size studies (n=109) & moderate & Indirect indices, but large sample size &  &  & 53 &  &  & few tens \\ 
collared lemming & 1995-2019, 2021-2022 & Rigorous density estimates at small spatial scale
(0.22 km2) extrapolated by habitat & moderate & Intensive sampling, but small spatial coverage and extrapolation by habitat &   0 & 39302 & 8128 & 10334 &  27 & few thousands to tens of thousands \\ 
brown lemming & 1995-2019, 2021-2022 & Rigorous density estimates at small spatial scale
(0.22 km2) extrapolated by habitat & moderate & Intensive sampling, but small spatial coverage and extrapolation by habitat &   0 & 447630 & 54043 & 93530 &  27 & few thousands to few hundreds of thousands \\ 
ermine & 1993-2019 & Indices of relative abundance derived from testimonials converted to abundance using home range size & moderate & Indirect indices and uncertainty on ermine home range size estimates &   8 & 156 & 40 & 37 &  27 & tens \\ 
long-tailed jaeger & 2004-2019, 2022 & Intensive nest monitoring (33 km2) extrapolated by habitat & high & Relatively large spatial coverage of sampling &   0 & 900 & 272 & 285 &  17 & units to few hundreds \\ 
red-throated loon & 2017-2019, 2022 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &  42 &  76 & 64 & 15 &   4 & few tens \\ 
Pacific loon & 2017-2019, 2022 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &   0 &   6 & 4 & 3 &   4 & units \\ 
tundra swan & 2017-2019, 2022 & Intensive study area-wide nest monitoring (389 km2) & high & No extrapolation &   0 &   2 & 1 & 1 &   4 & units \\ 
common-ringed plover & 2015-2017 & Nest monitoring on the main breeding sites & moderate & Intensive monitoring, but not exhaustive to study area &  44 &  62 & 55 & 9 &   3 & few tens \\ 
black-bellied plover & mean & Derived from the abundance estimate of American golden-plover using transects observations & moderate & Derived from high quality estimate of another species &  &  & 22 &  &  & few tens \\ 
black-bellied plover & mean & Derived from the abundance estimate of American golden-plover using incidental observations & moderate & Derived from high quality estimate of another species &  &  & 61 &  &  & few tens \\ 
Lapland longspur & mean & Extrapolation from intensive nest monitoring (2 km2)
and transects observations (R2=0.62, p=0.1, n=8) & moderate & Uncertain relation with large scale indices &  &  & 7110 &  &  & few thousands \\ 
Baird's sandpiper & mean & Extrapolation from intensive nest monitoring (2 km2)
and transects observations (R2=0.38, p=0.35, n=8) & moderate & Uncertain relation with large scale indices &  &  & 2495 &  &  & several hundreds to few thousands \\ 
sandhill crane & mean & Extrapolation from intensive nest monitoring (8 km2) and transect observations & moderate & Uncertain relation with large scale indices &  &  & 34 &  &  & few tens \\ 
king eider & mean & Intensive, but opportunistic nest monitoring (8 km2) extrapolated by habitat & moderate & Intensive, but opportunistic monitoring at relatively small spatial scale &  &  & 25 &  &  & tens \\ 
king eider & mean & Derived from the abundance estimate of red-throated loon using incidental observations & moderate & Derived from high quality estimate of another species &  &  & 106 &  &  & tens \\ 
long-tailed duck & mean & Intensive, but opportunistic nest monitoring (8 km2) extrapolated by habitat & moderate & Intensive, but opportunistic monitoring at relatively small spatial scale &  &  & 20 &  &  & tens \\ 
long-tailed duck & mean & Derived from the abundance estimate of red-throated loon using incidental observations & moderate & Derived from high quality estimate of another species &  &  & 191 &  &  & tens \\ 
rock ptarmigan & mean & Intensive, but opportunistic nest monitoring (8 km2) extrapolated to study area & low & Intensive, but opportunistic monitoring at relatively small spatial scale and prime nesting habitat not well sampled &  &  & 24 &  &  & tens \\ 
horned lark & mean & Derived from the abundance estimate of Lapland longspur using transects observations & low & Derived from moderate quality estimate of another species &  &  & 362 &  &  & few hundreds \\ 
horned lark & mean & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 411 &  &  & few hundreds \\ 
ruddy turnstone & mean & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 40 &  &  & tens \\ 
ruddy turnstone & mean & Derived from the abundance estimate of Bairds sandpiper using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 54 &  &  & tens \\ 
red phalarope & mean & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 156 &  &  & tens \\ 
red phalarope & mean & Derived from the abundance estimate of Bairds sandpiper using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 276 &  &  & tens \\ 
red knot & mean & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 64 &  &  & tens \\ 
red knot & mean & Derived from the abundance estimate of Bairds sandpiper using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 237 &  &  & tens \\ 
white-rumped sandpiper & mean & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 1135 &  &  & hundreds \\ 
white-rumped sandpiper & mean & Derived from the abundance estimate of Bairds sandpiper using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 1156 &  &  & hundreds \\ 
buff-breasted sandpiper & mean & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 41 &  &  & tens \\ 
buff-breasted sandpiper & mean & Derived from the abundance estimate of Bairds sandpiper using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 8 &  &  & tens \\ 
pectoral sandpiper & mean & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 79 &  &  & tens \\ 
pectoral sandpiper & mean & Derived from the abundance estimate of Bairds sandpiper using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 260 &  &  & tens \\ 
parasitic jaeger & mean & Maximum number of nest found annually during study area-wide opportunistic nest monitoring & low & Uncertainty about number of non-breeding individuals  &  &  & 17 &  &  & few tens \\ 
parasitic jaeger & mean & Maximum number of individuals banded in a year & low & Based on a single year and potentially not all individuals were captured &  &  & 8 &  &  & few tens \\ 
common raven & mean & Derived from the abundance estimate of glaucous gull using transects observations & low & Derived from moderate quality estimate of another species, but potential difference in detectability between species &  &  & 14 &  &  & few tens \\ 
common raven & mean & Derived from the abundance estimate of glaucous gull using incidental observations & low & Derived from moderate quality estimate of another species, but potential difference in detectability between species &  &  & 31 &  &  & few tens \\ 
American pipit & mean & Derived from the abundance estimate of Lapland longspur using transects observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 53 &  &  & tens to few hundreds \\ 
American pipit & mean & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 87 &  &  & tens to few hundreds \\ 
snow bunting & mean & Derived from the abundance estimate of Lapland longspur using transects observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 18 &  &  & few hundreds \\ 
snow bunting & mean & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 276 &  &  & few hundreds \\ 
Arctic hare & mean & Derived from the abundance estimate of Arctic fox using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 6 &  &  & few tens \\ 

@@

\end{longtable}

@@
